Two measures are better than one: Combining iconicity ratings and guessing experiments for a more nuanced picture of iconicity in the lexicon

### 2022-01-26 paper.Rmd
finished first draft

---
title: "Two measures are better than one: Combining iconicity ratings and guessing experiments for a more nuanced picture of iconicity in the lexicon"
output:
  bookdown::word_document2:
    reference_docx: wordstyles.docx
    toc: true
    toc_float: true
    number_sections: true
    css: custom.css
always_allow_html: true
bibliography: sources.bib

@@

```{r packages, include=FALSE}
library(tidyverse)
library(kableExtra)
library(bookdown)
library(report)
library(lmerTest)
library(plotly)
library(corrr)
library(boot)
library(zeallot)
library(pander)
library(sjPlot)
library(ggeffects)
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message = FALSE)
```

@@

@@

To discover how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches. Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools` [(https://pypi.org/project/icotools/)](https://pypi.org/project/icotools/), with support for a variety of stimulus formats (audio, video, and images). This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between future studies.

@@

For the pilot version of the guessing task, in which participants had to match a given form to its correct meaning, data from 3 out of 132 participants was excluded. In one case, the participant indicated that they were choosing the translations based on whether they sounded similar to the Japanese word (rather than based on their meaning). In the other two cases, the participants did not provide a task description and performed poorly on the control items, so the data was excluded as it was not clear that they were paying attention/understood the task correctly. In the new version of the guessing task, in which participants had to match a given meaning to its correct form, data from 3 out of 332 participants was excluded. In all three cases, the participants performed poorly on the control items and either did not provide a task description, or their task descriptions were irrelevant (they commented that the task was 'interesting' or 'difficult' instead of describing what they were doing in the task).   [COME BACK TO THIS POINT IT'S GOOD THE NEW GUESSING TASK PEOPLE SEEM TO UNDERSTAND IT BETTER]

@@

[OF THE THREE VERSIONS OF THE TASK, I THINK MATCHING THE WORD IS INTUITIVELY EASIEST FOR PARTICIPANTS TO UNDERSAND]
[I LOOKED AT REACTION TIMES AS WELL BUT THERE WERE ONLY TWO TRUE OUTLIERS IN THE WHOLE DATASET AND THEY WERE FOR PRACTICE ITEMS SO I COULDN'T BE BOTHERED DOING IT]

@@

```{r guessingtrans, fig.cap="Guessing task - guessing between translations"}
knitr::include_graphics("images/guessingtransdemo.PNG")
```

The same formulaic structure, "After X, Y", was used for all the sentences--where Y is the target perception and X is the event that causes it. As some sensory modalities (e.g. sound) may better lend themselves to the construal of iconicity than others (e.g. taste), correct translations were always paired with foil translations from the same modality (e.g. sound translations were only paired with other sound translations, and taste translations with other taste translations, etc.). To make the difficulty of the task comparable between different trials, only words that were neither synonyms nor antonyms of the correct translation were chosen as foils. Finally, the length of the sentences was also kept consistent (to a difference of no more than 5 characters) between pairings of translations and foils.

To test the robustness of the guessing procedure to different choices of translation and foil words, the same words were tested multiple times with different translations and foils. We were concerned that participants could choose particular translations because of how they sound (particularly if they sounded similar to the Japanese word), rather than based on their meanings as we intended. So, to minimise any potential effects from this, as much as possible phonologically distinct synonyms were chosen as alternative translations (e.g. SMALL|TINY, BIG|LARGE).

@@

```{r weirdcases}
guesses_trans%>%
  mutate(word_spec=paste(word,concept,sep="_"))->guesses_trans

@@

```{r guessingwords, fig.cap="Guessing task - guessing between words"}
knitr::include_graphics("images/guessingwords.PNG")
```

@@

```{r guessingwordsspec, fig.cap="Guessing task - guessing between words"}
knitr::include_graphics("images/guessingwordsspec.PNG")
```

@@

Since /a/ is often the most phonologically distant vowel from many of the vowels in the Japanese sound system, to avoid the foil words all having similar vowels, a different approach was used for substituting vowels. Instead of using feature values, vowels were substituted with the vowel obtained by rotating the vowel space 180 clockwise or counterclockwise. So /u/ is substituted with either /a/ or /i/, and /a/ is substituted with either /i/ or /u/ (see Figure \@ref(fig:vowels)).

```{r vowels,fig.cap="Vowel substitutions for the creation of foil words"}
knitr::include_graphics("images/vowels.PNG")
```

Finally, reduplicated words were ‘unreduplicated’ when creating foil words. For example, the foils for *fuwafuwa* were *watʃi*, *nati* and *ridːu* (not *watʃiwatʃi*, *natinati* and *ridːuridːu*).

@@

```{r ratingdemo, fig.cap="Rating task"}
knitr::include_graphics("images/ratingdemo.PNG")
```

@@

# Statistical analyses

Statistical analyses were conducted using `R.Version()$version.string`.

@@

# we used this binomial test to figure out how many correct guesses (out of 30) were needed to have a result significantly different from chance--it's 21
#binom.test(21,30,p=.5)

randomfoils <- read_csv("responses-randomfoils.csv")

@@

words <- randomres$identifier
replace(words,words=="zoNzoN_SHIVERING","zoNzoN_(SPINE) TINGLING")
replace(words,words=="genki_LIVELY","geNki_LIVELY (ENERGETIC)")

zyiNzyiN_POUNDING (HEAD)

guesses_words%>%
  group_by(identifier)%>%
  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
  select(form,score)%>%unique()->oppres

comparison <- left_join(randomres,oppres,by="identifier")%>%
  rename(random_foils=score.x,opp_foils=score.y)%>%unique()

@@

table(comparison$design,comparison$`above chance`)
#chisq.test(table(comparison$design,comparison$`above chance`))
```

We also compared the distributions of guessing accuracies and mean iconicity ratings between the different methods. Since the iconicity ratings in this study were collected from naive participants who did not speak any Japanese, whereas rating studies more commonly use native speaker participants, I added one more plot to the figure showing the distribution of iconicity ratings in a separate study by Thompson et al. [-@thompson_iconicity_2020]. Thompson et al. collected iconicity ratings for Japanese words from native Japanese speaking participants. Their dataset contained a wider variety of words than the current dataset, and they also used a different scale. Their scale went from -5 'antiiconic' to 5 'iconic', with 0 being labelled as 'arbitrary'. The scale in this study started at 0 (also labelled as 'arbitrary', or "no resemblance between the word and its meaning"), and went up to 6 for "strong resemblance between the word and meaning". To make the data more comparable between the two studies, and because previous studies have found the negative ratings unreliable [@motamedi_iconicity_2019], I have filtered the data from Thompson et al. to only contain responses using the part of the scale between 0 and 5. I have also filtered the words to only contain verbs, adverbs, and adjectives from the Yamato stratum. The Yamato stratum refers to the native lexicon of Japanese. Thompson et al.'s study included both words from the Yamato stratum, as well as Sino-Japanese and foreign words. This study only included Yamato words, and predominantly these were verbs, adverbs and adjectives. Both the data in this study and in Thompson et al. 2020 contains a mix of ideophones and non-ideophones within the Yamato stratum. Finally, ratings from both studies were transformed so that they varied between 0 and 1, to match with the guessing accuracies. The resulting distributions are shown in Figure \@ref(fig:discriminability)

```{r discriminability,fig.cap="Discriminability of different measures"}
oppres%>%
  mutate(method="guesses between words")%>%
  unique()->oppres

@@

Focusing first on the data from the current study, we can see that a greater spread of measures is provided by the guesses compared to the ratings, and that within the guesses, the method of guessing between words provides a better spread of measures than guessing between translations--both at the very high end of the scale (highly guessable words) and at the very low end of the scale (poorly guessable words). However, if we look at the ratings from native Japanese speakers, these have a pretty equivalent spread to the guesses between words. Their distribution is slightly narrower at the very top end of the scale. However, the data from the current study was chosen from a domain known to be high in iconicity, whereas the data from Thompson et al. was more varied, with proportionally less ideophones. Thus, this could well be simply a reflection of the differences between the two datasets rather than relating to the methods used.

@@

Figure \@ref(fig:comparison) compares the guessing accuracies and mean iconicity ratings, for both ideophones and non-ideophones. The words in the pilot study where participants were guessing between translations were different to the words in the subsequent guessing and rating studies, so here only the results from the later guessing study (where participants guessed between words) are shown. At the top end of the scale, the two measures agree--ideophones score higher than non-ideophones for both measures. However, at the bottom of the scale something strange happens. While in the ratings, the bottom of the scale is dominated by non-ideophones (as expected), in the guesses, the bottom of the scale is actually dominated by *ideophones*. That is, ideophones are simultaneously guessed *better* and *worse* than non-ideophones. We will return to this in the discussion.

```{r comparison,fig.cap="Comparison of guesses and ratings, for ideophones and non-ideophones"}
# get info on ideophones
words <- read_csv("wordlist.csv")
words%>%
  select(form,ideophone)->info

@@

library(gridExtra)
comparison_dat%>%
  filter(method=="ratings")%>%
  mutate(mean_rating=6*score)%>%
  mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
  ggplot(aes(x=word_type,y=mean_rating))+geom_violin()+theme_classic()+ylim(0,6)+labs(x="Word type",y="Mean rating")->plot1

@@

For both ideophones and non-ideophones, there was a strong correlation between the ratings and the guesses. This correspondence was slightly better for the ideophones (r = 0.65, 95% CI [0.44, 0.79], t(43) = 5.57, p < .001) than for the non-ideophones (r = 0.43, 95% CI [0.23, 0.60], t(71) = 4.06, p < .001). To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, ideophone status, and the interaction between these two factors, and a second model predicting ratings from guesses, ideophone status, and the interaction between these two factors. Both models again used the z-scores rather than the raw ratings and guesses.

@@

```{r bootstrap function, eval=FALSE}
info <- read_csv("wordlist.csv")%>%select(form,ideophone)
# my ratings from English people
ratings%>%
  group_by(identifier)%>%
  mutate(mean_rating=mean(rating))%>%
  select(iconicityM=mean_rating,rating,prolificID)%>%
  mutate(task="current study")%>%
  mutate(form=str_split(identifier,"_")[[1]][1])%>%
  left_join(info,by="form")%>%
  ungroup()%>%
  unique()%>%
  select(-form,-identifier,-prolificID)->ratingdat

@@

```{r run bootstrap, cache=TRUE, message=FALSE, warning=FALSE, eval=FALSE}

@@

```{r make person-total graph, eval=FALSE}
cis %>% 
  ggplot(aes(x=name,
             y=r,
             ymin=lower,
             ymax=upper,
             color=sign)) +
  geom_point(position=position_dodge(0.1)) +
  geom_errorbar(position=position_dodge(0.1),
                width=0.1) + 
  coord_flip() +ylim(0,0.6)+theme_classic()+labs(y="Correlation (r)",x="")->plot
plot
```

```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%"}
knitr::include_graphics("images/persontotal.svg")
```

@@

While ideophones and non-ideophones with high iconicity ratings were generally guessed equally well, there was an interaction effect such that ideophones with low iconicity ratings were guessed *worse* than non-ideophones with comparable ratings. Low iconicity ratings in non-ideophones generally correspond to chance guessing accuracy--reflecting a lack of associations--whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy--reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones. The result highlights the subjective nature of form-meaning associations, and that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers.

Poor guessing accuracies could be explained by conflicting, non-resemblance based associations. For example, one person commented that *zarazara* as a word for ‘ROUGH’ sounds wrong to them because they associate the word *zara* with the clothing store ZARA, and clothes are soft. These could be masking either a lack of resemblance between form and meaning, or a resemblance between form and meaning that is ignored in the face of the conflicting association. Of course, conversely one could argue that high guessing accuracies could then *also* be explained by non-resemblance based associations. Fortunately, the chances of English speakers having the *same* form-meaning association as Japanese speakers based on something random (like the name of a clothing store) should be much smaller than the chances of them having a *different* association. Thus, if they do exist, we predict that the majority of non-resemblance based associations should be reflected in poorer rather than higher guessing accuracies.

That the poor guessing results also corresponded to lower ratings suggests that these ratings also likely reflect form-meaning *associations*, rather than form-meaning *resemblances* specifically. This is despite the instructions in the task specifically asking about resemblances. That participants in rating studies do not distinguish iconicity from indexicality or other kinds of associations is hardly surprising, given these are distinctions even seasoned semioticians can find a struggle. Nor is it necessarily problematic; whether the association is based on resemblance or other factors, the end result it the same--a bias. However, it is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important, since associations are much more dependent on world experience than resemblances [see also @motamedi_iconicity_2019: 17].

Even resemblance itself is not entirely objective, though this is often an assumption of rating and guessing studies. In the beginning of this study, we defined iconicity as involving *perceived* resemblances, reflecting a conception of iconicity not as an objective property of signs, but as a subjective process involving construal (Occhino et al. 2017; Occhino, Anible, and Morford 2020). Occhino et al. [-@occhino_role_2020: 117] provide an excellent illustration of this in the ASL sign for dance, which involves an inverted V-handshape. On its own, the meaning of this sign is unlikely to be transparent to non-signers. However, a signer will recognise the inverted-V handshape from a network of signs involving the construal of a pair of legs mapped to a pair of extended fingers--such as in the sign STAND, which is likely to be transparent to non-signers. Thus, iconicity can be both language-internal (as in the sign for DANCE) and/or language-external (as in the sign for STAND). However, guessing studies and rating tasks with non-speakers will only pick up on examples of language-external iconicity, while language-internal iconicity falls under the radar.

It is even possible that different construals could lead to non-speakers having exactly the *opposite* iconic mapping to the mapping in the language under study. This is perhaps more likely in spoken than in signed languages, particularly where phoneme inventories are small. The most famous example comes from vowel-size sound symbolism. The most common mapping relates high vowels--like /i/--to smallness, and low vowels--like /a/--to largeness [@ultan_size-sound_1978]. However, a few languages also show the *reverse* mapping--two examples are Korean and Bahnar [@shinohara_cross-linguistic_2010; @difflothibig_1994]. Different construals make it possible for both mappings to be perceived as iconic to speakers, and in fact this is likely since the reverse mappings are actually reported in ideophones--which speakers generally perceive as iconic [@thompson_iconicity_2020]. For example, a construal of the change from /i/ to /a/ as involving an *expansion* of the space in the oral cavity could lead to the /i/-small, /a/-large mapping. However, one could also construe the same event as involving the *contraction* of the space occupied by the tongue, resulting in an /i/-large, /a/-small mapping. Interestingly, despite the conflicting mapping in their own language, when evaluating non-words Korean speakers still show a preference for the /i/-small, /a/-big mapping [@shinohara_cross-linguistic_2010]. This is encouraging as it suggests that when judging unfamiliar stimuli, conflicting mappings in the participants own languages are unlikely to hide iconic effects in cases where the naturalness of the mapping is very strong [as in the /i/-small, /a/-big example; @ultan_size-sound_1978]

Finally, the comparison between guesses and ratings highlights a bias in the design of the rating task, as all the words in the data were in the end rated as "slightly" iconic (even by non-speakers), whereas the guessing results show that a good number of these were not guessed any better than chance. This is probably an artefact of the design of the rating task, in which "arbitrary" is only 1 of the 7 or 10 points on the scale--the rest indicating varying degrees of form-meaning resemblance. This is not so problematic, as the ratings still correlate with guessing accuracy, indicating that the relative differences in iconicity still hold. However, it highlights that interpretations of (particularly low) ratings as reflections of iconicity should be taken with a grain of salt.

@@

Given the limitations of each measure discussed above, for a full picture of iconicity in the lexicon, a synthesis of measures is recommended. Iconicity ratings from native speakers can tell us which mappings are meaningful to them, while comparisons with guessability for non-speakers can establish which of these mappings are likely to be meaningful on their own, versus which *become* meaningful through experience with the rest of the lexicon (language-external versus language-internal iconicity). @occhino_role_2020 found differential effects of these two types of mappings in sign processing by signers of different proficiencies. They found that both types of iconicity were helpful to signers of a lower proficiency, but that for highly proficient signers only the most pervasive, language-external mappings made a difference to processing. Guessing and rating comparisons could also be useful to explore the influence of structural markedness on iconicity effects. Since structural markedness appears to boost ratings but not guessability, the two measures could be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects. We tend to assume that iconic effects are driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks. Since structural markedness is also subjective, the choice of participants used in the rating task should be theoretically justified and matched to the phenomenon the measures will be used to study. For example, if the measures will be used to study language processing in adults, then adult native speakers should be used. Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g. arbitrarily dividing the scale at the half-way point, or using percentiles tied to particular datasets.

@@

We also sought to evaluate different rating and guessing paradigms, and were able to make some methodological improvements--particularly to the guessing design. We contrasted two different guessing paradigms--one where participants are given a word and have to match it to the correct meaning from two translations, and another where participants are given a meaning and have to match it to the correct word from two words. Content-wise, choosing between words is more comparable to the design of a rating task, as both give the meaning first and involve only one English translation. This is important as the use of translations leads to several complications in the experiment design. First, English-speaking participants can be expected to have more associations with English words than with unknown Japanese words, which could make the task more sensitive to the particular translations chosen. In addition, care has to be taken when choosing foils as well, as they should preferably be from the same semantic domain, of a similar length of characters, and not synonyms or antonyms of the correct translation. This makes the guessing between translations design more difficult to use, particularly in small semantic domains (e.g. taste). In contrast, a task in which participants guess between words is much easier to operationalise. This design can be easily adopted to any semantic domain or any kind of data, and the foils can be chosen either randomly from the other trials or selected based on specific criteria. In our case we chose foils that were phonologically as distinct as possible from the word being tested. The first reason for this was theoretical: in a task designed to pick up on form-meaning resemblance, words that sound very different should not be suited to that meaning, enhancing the effect of iconicity. The second was practical: our stimuli had artificially flat intonations, which has been shown to decrease performance in guessing studies [@kunihira_effects_1971; @dingemanse_what_2016]. By creating opposite sounding words, we tried to increase performance in the guessing task despite the degraded stimuli.

>>>>

---
title: "Two measures are better than one: Combining iconicity ratings and guessing experiments for a more nuanced picture of iconicity in the lexicon"
output:
  bookdown::html_document2:
   # reference_docx: wordstyles.docx
    toc: true
    toc_float: true
    number_sections: true
    css: custom.css
    code_folding: hide
always_allow_html: true
bibliography: sources.bib

@@

```{r packages, include=FALSE}
library(tidyverse)
library(kableExtra)
library(bookdown)
library(report)
library(lmerTest)
library(plotly)
library(corrr)
library(boot)
library(zeallot)
library(pander)
library(sjPlot)
library(ggeffects)
library(gridExtra)
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
```

@@

**Keywords:** iconicity, ideophones, lexical norms, iconicity ratings, guessability

@@

To discover how to get the most out of each measure, we compare and contrast different rating and guessing paradigms, and in particular introduce a new guessing paradigm that improves on the robustness, discriminability and sensitivity of previous approaches. Finally, to promote the use of these new measures, we introduce a reproducible workflow for automatically generating rating and guessing experiments in a standardised format, via a python package `icotools`, with support for a variety of stimulus formats (audio, video, and images). This will make the collection of behavioural based iconicity measures quicker, easier, and more comparable between future studies.

@@

For the pilot version of the guessing task, in which participants had to match a given form to its correct meaning, data from 3 out of 132 participants was excluded. In one case, the participant indicated that they were choosing the translations based on whether they sounded similar to the Japanese word (rather than based on their meaning). In the other two cases, the participants did not provide a task description and performed poorly on the control items, so the data was excluded as it was not clear that they were paying attention/understood the task correctly. In the new version of the guessing task, in which participants had to match a given meaning to its correct form, data from 3 out of 332 participants was excluded. In all three cases, the participants performed poorly on the control items and either did not provide a task description, or their task descriptions were irrelevant (they commented that the task was 'interesting' or 'difficult' instead of describing what they were doing in the task).

@@

@@

```{r guessingtrans, fig.cap="Guessing task - guessing between translations",echo=FALSE}
knitr::include_graphics("images/guessingtransdemo.PNG")
```

The same formulaic structure, "After X, Y", was used for all the sentences--where Y is the target perception and X is the event that causes it. As some sensory modalities (e.g. sound) may better lend themselves to the construal of iconicity than others (e.g. taste), correct translations were always paired with foil translations from the same modality (e.g. sound translations were only paired with other sound translations, and taste translations with other taste translations, etc.). To make the difficulty of the task comparable between different trials, only words that were neither synonyms nor antonyms of the correct translation were chosen as foils. Finally, the length of the sentences was also kept consistent (to a difference of no more than 5 characters) between pairings of translations and foils. 
To test the robustness of the guessing procedure to different choices of translation and foil words, the same words were tested multiple times with different translations and foils. We were concerned that participants could choose particular translations because of how they sound (particularly if they sounded similar to the Japanese word), rather than based on their meanings as we intended. So, to minimise any potential effects from this, as much as possible phonologically distinct synonyms were chosen as alternative translations (e.g. SMALL|TINY, BIG|LARGE).

@@

```{r weirdcases,echo=FALSE}
guesses_trans%>%
  mutate(word_spec=paste(word,concept,sep="_"))->guesses_trans

@@

```{r guessingwords, fig.cap="Guessing task - guessing between words",echo=FALSE}
knitr::include_graphics("images/guessingwords.PNG")
```

@@

```{r guessingwordsspec, fig.cap="Guessing task - guessing between words",echo=FALSE}
knitr::include_graphics("images/guessingwordsspec.PNG")
```

@@

Since /a/ is often the most phonologically distant vowel from many of the vowels in the Japanese sound system, to avoid the foil words all having similar vowels, a different approach was used for substituting vowels. Instead of using feature values, vowels were substituted with the vowel obtained by rotating the vowel space 180 clockwise or counterclockwise. So /u/ is substituted with either /a/ or /i/, and /a/ is substituted with either /i/ or /u/ (see Figure \@ref(fig:vowels)). Finally, reduplicated words were ‘unreduplicated’ when creating foil words. For example, the foils for *fuwafuwa* were *watʃi*, *nati* and *ridːu* (not *watʃiwatʃi*, *natinati* and *ridːuridːu*).

```{r vowels,fig.cap="Vowel substitutions for the creation of foil words",echo=FALSE}
knitr::include_graphics("images/vowels.PNG")
```

@@

```{r ratingdemo, fig.cap="Rating task",echo=FALSE}
knitr::include_graphics("images/ratingdemo.PNG")
```

@@

# Results

Statistical analyses were conducted using `r R.Version()$version.string`.

@@

# we used this binomial test to figure out how many correct guesses (out of 30) were needed to have a result significantly different from chance--it's 21
#binom.test(21,30,p=.5)
randomfoils <- read_csv("responses-randomfoils.csv")

@@

# fix up some naming differences
words <- randomres$identifier
words <- replace(words,words=="zoNzoN_SHIVERING","zoNzoN_(SPINE) TINGLING")
words <- replace(words,words=="geNki_LIVELY","geNki_LIVELY (ENERGETIC)")

guesses_words%>%
  filter(identifier %in% words|form=="zyiNzyiN")%>%
  group_by(identifier)%>%
  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
  ungroup()%>%
  select(form,score)%>%unique()->oppres

comparison <- left_join(randomres%>%select(-identifier),oppres,by="form")%>%
  rename(random_foils=score.x,opp_foils=score.y)%>%unique()

@@

#table(comparison$design,comparison$`above chance`)
#chisq.test(table(comparison$design,comparison$`above chance`))
```

We also compared the distributions of guessing accuracies and mean iconicity ratings between the different methods. Since the iconicity ratings in this study were collected from naive participants who did not speak any Japanese, whereas rating studies more commonly use native speaker participants, I added one more plot to the figure showing the distribution of iconicity ratings in a separate study by Thompson et al. [-@thompson_iconicity_2020]. Thompson et al. collected iconicity ratings for Japanese words from native Japanese speaking participants. Their dataset contained a wider variety of words than the current dataset, and they also used a different scale. Their scale went from -5 'antiiconic' to 5 'iconic', with 0 being labelled as 'arbitrary'. The scale in this study started at 0 (also labelled as 'arbitrary', or "no resemblance between the word and its meaning"), and went up to 6 for "strong resemblance between the word and meaning". To make the data more comparable between the two studies, and because previous studies have found the negative ratings unreliable [@motamedi_iconicity_2019], I have filtered the data from Thompson et al. to only contain responses using the part of the scale between 0 and 5. I have also filtered the words to only contain verbs, adverbs, and adjectives from the Yamato stratum. The Yamato stratum refers to the native lexicon of Japanese. Thompson et al.'s study included both words from the Yamato stratum, as well as Sino-Japanese and foreign words. This study only included Yamato words, mainly verbs, adverbs and adjectives. Both the data in this study and in Thompson et al. 2020 contains a mix of ideophones and non-ideophones within the Yamato stratum. Finally, ratings from both studies were transformed so that they varied between 0 and 1, to match with the guessing accuracies. The resulting distributions are shown in Figure \@ref(fig:discriminability)

```{r discriminability,fig.cap="Discriminability of different measures"}
guesses_words%>%
  group_by(identifier)%>%
  mutate(score=sum(answer=="correct")/sum(answer=="correct"|answer=="incorrect"))%>%
  select(identifier,score)%>%
  unique()%>%
  mutate(method="guesses between words")->oppres

@@

Focusing first on the data from the current study, we can see that a greater spread of measures is provided by the guesses compared to the ratings, and that within the guesses, the method of guessing between words provides a better spread of measures than guessing between translations--both at the very high end of the scale (highly guessable words) and at the very low end of the scale (poorly guessable words). However, if we look at the ratings from native Japanese speakers, these have a pretty equivalent spread to the guesses between words. Their distribution is slightly narrower at the very top end of the scale. However, the data from the current study was chosen from a domain known to be high in iconicity, whereas the data from Thompson et al. was more varied, with proportionally less ideophones. Thus, this could simply be a reflection of the differences between the two datasets rather than relating to the methods used.

@@

Figure \@ref(fig:comparison) compares the guessing accuracies and mean iconicity ratings, for both ideophones and non-ideophones. The words in the pilot study where participants were guessing between translations were different to the words in the subsequent guessing and rating studies, so here only the results from the later guessing study (where participants guessed between words) are shown. At the top end of the scale, the two measures agree--ideophones score higher than non-ideophones for both measures. However, at the bottom of the scale something strange happens. While for the ratings, the bottom of the scale is dominated by non-ideophones (as expected), for the guesses, the bottom of the scale is actually dominated by *ideophones*. That is, ideophones are simultaneously guessed *better* and *worse* than non-ideophones. We will return to this in the discussion.

```{r comparison,fig.cap="Comparison of guesses and ratings, for ideophones and non-ideophones"}
# get info on ideophones
words <- read_csv("ideophone_list.csv")
words%>%
  select(form,ideophone)->info

@@

comparison_dat%>%
  filter(method=="ratings")%>%
  mutate(mean_rating=6*score)%>%
  mutate(word_type=ifelse(ideophone=="y","ideophones","non-ideophones"))%>%
  ggplot(aes(x=word_type,y=mean_rating))+geom_violin()+theme_classic()+ylim(0,6)+labs(x="Word type",y="Mean rating")->plot1

@@

For both ideophones and non-ideophones, there was a strong correlation between the ratings and the guesses. This correspondence was slightly better for the ideophones (r = 0.66, 95% CI [0.44, 0.79], 95% CI [0.53, 0.76], t(99) = 8.68, p < .001) than for the non-ideophones (r = 0.41, 95% CI [0.29, 0.52], t(201) = 6.45, p < .001). To explore this relationship further, we created two linear regression models: one predicting guesses from ratings, ideophone status, and the interaction between these two factors, and a second model predicting ratings from guesses, ideophone status, and the interaction between these two factors. Both models again used the z-scores rather than the raw ratings and guesses. The models were created using the R package `lmerTest` (version `r packageVersion("lmerTest")`) [@lmertest].

@@

```{r bootstrap function,cache=TRUE,eval=FALSE}
# my ratings from English people
ratings%>%
  group_by(identifier)%>%
  mutate(mean_rating=mean(rating))%>%
  select(iconicityM=mean_rating,rating,prolificID)%>%
  mutate(task="current study")%>%
  mutate(form=str_split(identifier,"_")[[1]][1])%>%
  left_join(info,by="form")%>%
  ungroup()%>%
  unique()%>%
  select(-form,-identifier,-prolificID)->ratingdat

@@

```{r run bootstrap, cache=TRUE, message=FALSE, warning=FALSE,eval=FALSE}

@@

```{r make person-total graph,eval=FALSE}
cis %>% 
  ggplot(aes(x=name,
             y=r,
             ymin=lower,
             ymax=upper,
             color=sign)) +
  geom_point(position=position_dodge(0.1)) +
  geom_errorbar(position=position_dodge(0.1),
                width=0.1) + 
  coord_flip() +ylim(0,0.6)+theme_classic()+labs(y="Correlation (r)",x="")->plot
plot
```

```{r ratingconsistency,fig.cap="Consistency between participants for iconicity ratings of ideophones versus non-ideophones",out.width="70%",echo=FALSE}
knitr::include_graphics("images/bootstrapping.png")
```

@@

While ideophones and non-ideophones with high iconicity ratings were generally guessed equally well, there was an interaction effect such that ideophones with low iconicity ratings were guessed *worse* than non-ideophones with comparable ratings. Low iconicity ratings in non-ideophones generally correspond to chance guessing accuracy--reflecting a lack of associations--whereas equivalent ratings in ideophones correspond to *below chance* guessing accuracy--reflecting *negative associations* masked in the rating results by the tendency to inflate ratings for ideophones. The result highlights the subjective nature of form-meaning associations, and that by taking above-chance guessing accuracy as a measure of iconicity we are only picking up on those associations that happen to correspond--and crucially not to conflict--between (in this case) English and Japanese speakers. This is something researchers should be aware of, because it means that decisions about *whom* to collect iconicity measurements from are very important.

Poor guessing accuracies could be explained by conflicting associations. For example, one person commented that *zarazara* as a word for ‘ROUGH’ sounds wrong to them because they associate the word *zara* with the clothing store ZARA, and clothes are soft. These could be masking either a lack of resemblance between form and meaning, or a resemblance between form and meaning that is ignored in the face of the conflicting association. Of course, conversely one could argue that high guessing accuracies could then *also* be explained by non-resemblance based associations. Fortunately, the chances of English speakers having the *same* form-meaning association as Japanese speakers based on something random (like the name of a clothing store) should be much smaller than the chances of them having a *different* association. Thus, if they do exist, we predict that the majority of non-resemblance based associations should be reflected in poorer rather than higher guessing accuracies. It is interesting that conflicting associations appear to have a stronger effect in ideophones (some of which were guessed at accuracies significantly below chance) than in non-ideophones (which were guessed below chance only rarely). Perhaps because participants are more likely to view form-meaning relationships in ideophones as meaningful (due to their structural markedness), they are more likely to attach conflicting associations to ideophones, leading to a stronger sense that the ideophone should correspond to the *opposite* of the given meaning.

Finally, the comparison between guesses and ratings highlights a bias in the design of the rating task, as all the words in the data were in the end rated as "slightly" iconic (even by non-speakers), whereas the guessing results show that a good number of these were not guessed any better than chance. This is probably an artefact of the design of the rating task, in which "arbitrary" is only 1 of the 7 or 10 points on the scale--the rest indicating varying degrees of form-meaning resemblance. This is not so problematic, as the ratings still correlate with guessing accuracy, indicating that the relative differences in iconicity still hold. However, it highlights that interpretations of particularly *low* iconicity ratings as reflections of iconicity should be viewed with caution.

@@

Given the limitations of each measure discussed above, for a full picture of iconicity in the lexicon, a synthesis of measures is recommended. Iconicity ratings from native speakers can tell us which mappings are meaningful to them, while comparisons with guessability for non-speakers can establish which of these mappings are likely to be meaningful on their own, versus which *become* meaningful through experience with the rest of the lexicon (language-external versus language-internal iconicity). @occhino_role_2020 found differential effects of these two types of mappings in sign processing by signers of different proficiencies. They found that both types of iconicity were helpful to signers of a lower proficiency, but that for highly proficient signers only the most pervasive, language-external mappings made a difference to processing.

Since structural markedness appears to boost ratings but not guessability, the two measures could also be used together to tease apart the influence of structural markedness versus form-meaning resemblances in driving iconic effects. Iconic effects are generally assumed to be driven by form-meaning resemblances, but since these often go together with structural markedness it would be useful to know the relative contribution of each factor in different situations and tasks. Since structural markedness is also subjective, the choice of participants used in the rating task will be important. Finally, having guesses alongside ratings would allow researchers to make better decisions about the cut-off point between "high" and "low" iconicity ratings, as these could be motivated by correlations with guessing accuracy, rather than e.g. arbitrarily dividing the scale at the half-way point, or using percentiles tied to particular datasets.

@@

We also sought to evaluate different rating and guessing paradigms, and were able to make some methodological improvements--particularly to the guessing design. We contrasted two different guessing paradigms--one where participants are given a word and have to match it to the correct meaning from two translations, and another where participants are given a meaning and have to match it to the correct word from two words. Content-wise, choosing between words is more comparable to the design of a rating task, as both give the meaning first and involve only one English translation. This is important as the use of translations leads to several complications in the experiment design. First, English-speaking participants can be expected to have more associations with English words than with unknown Japanese words, which could make the task more sensitive to the particular translations chosen. In addition, care has to be taken when choosing foils as well, as they should preferably be from the same semantic domain, of a similar length of characters, and not synonyms or antonyms of the correct translation. This makes the guessing between translations design more difficult to use, particularly in small semantic domains (e.g. taste).

In contrast, a task in which participants guess between words is much easier to operationalise. This design can be easily adopted to any semantic domain or any kind of data, and the foils can be chosen either randomly from the other trials or selected based on specific criteria. In our case we chose foils that were phonologically as distinct as possible from the word being tested. The first reason for this was theoretical: in a task designed to pick up on form-meaning resemblance, words that sound very different should not be suited to that meaning, enhancing the effect of iconicity. The second was practical: our stimuli had artificially flat intonations, which has been shown to decrease performance in guessing studies [@kunihira_effects_1971; @dingemanse_what_2016]. By creating opposite sounding words, we tried to increase performance in the guessing task despite the degraded stimuli.
